Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-07-30 ms.tex
a little more text on RPF vs RPI

\begin{figure*}
{\gridline{\fig{rpf_vs_rpi_old_cds_no_refpix.pdf}{0.99\textwidth}{No Reference Pixels RPF}}}
{\gridline{\fig{rpf_vs_rpi_new_cds_with_refpix.pdf}{0.99\textwidth}{Reference Pixel RPF}}}
\caption{Reset per frame with reference pixel correction.}\label{fig:RPFrefpix}
\end{figure*}

@@

\begin{figure*}
{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.33\textwidth}{Reset-per-frame, 2048x256}
\fig{azlab_ratio_tser_RPI.pdf}{0.33\textwidth}{Reset-per-integration, 2048x256}}}
{\gridline{\fig{azlab_ratio_tser_stripe64_1p5_mA_rpt2.pdf}{0.33\textwidth}{Reset-per-frame, 2048x64}
\fig{azlab_ratio_tser_stripe64_1p5_mA_rpt3rpi.pdf}{0.33\textwidth}{Reset-per-integration, 2048x64}}}
\caption{Reset per integration versus reset per frame.}\label{fig:subarraySizes}
\end{figure*}

>>>>

\begin{figure*}
{\gridline{\fig{rpf_vs_rpi_old_cds_no_refpix.pdf}{0.8\textwidth}{No Reference Pixels RPF}}}
{\gridline{\fig{rpf_vs_rpi_new_cds_with_refpix.pdf}{0.8\textwidth}{Reference Pixel RPF}}}
\caption{Reset per frame with reference pixel correction.}\label{fig:RPFrefpix}
\end{figure*}

As a further demonstration that reference pixels can subtract amplifier offsets or background subtraction, we show time series for tests with a reset per frame and a reset per integration in Figure \ref{fig:RPFvsRPItseries}.
The resets-per-frame have similar noise to the resets-per-integration on short timescales.
For the 2048x256 subarray, the standard deviation were 197 ppm and 183 ppm for RPF and RPI respectively.
For the 2048x64 subarray, the standard deviations were 327 ppm and 180 ppm for RPF and RPI respectively.
The difference between these is dominated by the slope through the test.
We suspect the flatter slow during RPI is a coincidence because the the resets within an integration (less than one minute) are unlikely to propagate a gradual slope over several hours.

\begin{figure*}
{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.33\textwidth}{Reset-per-frame, 2048x256}
\fig{azlab_ratio_tser_RPI.pdf}{0.33\textwidth}{Reset-per-integration, 2048x256}}}
{\gridline{\fig{azlab_ratio_tser_stripe64_1p5_mA_rpt2.pdf}{0.33\textwidth}{Reset-per-frame, 2048x64}
\fig{azlab_ratio_tser_stripe64_1p5_mA_rpt3rpi.pdf}{0.33\textwidth}{Reset-per-integration, 2048x64}}}
\caption{Reset per integration versus reset per frame.}\label{fig:RPFvsRPItseries}
\end{figure*}

@@
